Ecuador plant species BIEN data

### 2022-10-26 code/L0/L0_Ecuador_plants_BIEN.Rmd
output summarytools results to html in output file path

### using summarytools package
```{r}
dfSummary(Ecuador_BIEN_occ, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
```

```{r}
dfSummary(Ecuador_BIEN_species_list, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
```

```{r}
dfSummary(Ecuador_BIEN_traits, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
```

>>>>

### using summarytools package
```{r}
Ecuador_BIEN_occ_summary <- dfSummary(Ecuador_BIEN_occ, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_BIEN_occ_summary, method = "render")
view(Ecuador_BIEN_occ_summary, file = file.path(output_path,"Ecuador_BIEN_occ_summary.html"))
```

```{r}
Ecuador_BIEN_species_list_summary <- dfSummary(Ecuador_BIEN_species_list, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_BIEN_species_list_summary, method = "render")
view(Ecuador_BIEN_species_list_summary, file = file.path(output_path,"Ecuador_BIEN_species_list_summary.html"))
```

```{r}
Ecuador_BIEN_traits_summary <- dfSummary(Ecuador_BIEN_traits, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(Ecuador_BIEN_traits_summary, method = "render")
view(Ecuador_BIEN_traits_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```
